\addcontentsline{toc}{chapter}{Bibliography}
\begin{thebibliography}{9}

\bibitem{progerlang}
  Joe Armstrong,
  \emph{Programming Erlang, Software for a Concurrent World}.
  The Pragmatic Programmers,
  Version: 2008-7-6.

\bibitem{erlangprog}
  Francesco Cesarini and Simon Thompson,
  \emph{Erlang programming}.
  O'Reilly Media,
  2009.

\bibitem{chord}
  Ion Stoica, Robert Morris, David Karger, M. Frans Kaashoek, Hari Balakrishnan,
  \emph{Chord: A Scalable Peer-to-peer Lookup Service for Internet Applications}.
  MIT Laboratory for Computer Science.

\bibitem{pastry}
  Antony Rowstron	and Peter Druschel,
  \emph{Pastry: Scalable, decentralized object location and routing for large-scale peer-to-peer systems}.
  Microsoft Research Ltd, St. George House.

\bibitem{kademila}
  Peter Maymounkov and David Mazieres,
  \emph{Kademilia: A Peer-to-peer Information System Based on the XOR Metric}.
  New York University.

\bibitem{tapestry}
  Ben Y. Zhao, Ling Huang, Jeremy Stribling, Sean C. Rhea, Anthony D. Joseph, Member, IEEE, and John D. Kubiatowicz, Member, IEEE,
  \emph{Tapestry: A Resilient Global-Scale Overlay for Service Deployment}.

\bibitem{dht}
  \emph{Wikipedia: Distributed Hash Tables}.
  http://en.wikipedia.org/wiki/Distributed\_hash\_table.
  
\bibitem{experimental_design}
  Dr David Evans
  \emph{Lecture notes on Experimental Design}.
  CS 457/657,	Winter 2005.

\bibitem{tcp}
  Serge Aleynikov,
  \emph{Building a Non-blocking TCP server using OTP principle}.
  TrapExit.org / http://www.trapexit.org/Building\_a\_Non-blocking\_TCP\_server\_using\_OTP\_principles.

\bibitem{gen_tcp}
  Andreas Stenius,
  \emph{gen\_listener\_tcp}.
  Github.org / https://github.com/kaos/gen\_listener\_tcp.

\bibitem{erlymock}
  Jason Wagner,
  \emph{erlymock}.
  Github.org / https://github.com/nialscorva/erlymock/wiki.

\bibitem{erlangtdd}
  Jason Wagner,
  \emph{Erlang, Testing and TDD}.
  http://erlcode.wordpress.com/.

\bibitem{webmachine}
  Basho,
  \emph{Webmachine documentation}.
  http://webmachine.basho.com/.

\end{thebibliography}
